Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-29 paper/ms.tex
More small updates to text
Update to many orbits caption

For the offset in the Solar radius {\em bottom panels}, the error is largest
for $J_r$, with some deviations resulting in $L_z$ and relatively small
deviations in $J_z$. In the {\em bottom left} panel the orange and blue lines
overlap, and in the {\em bottom middle} and {\em bottom right} panels all
three lines overlap.

\begin{figure*}
\plotone{fig/schmactions_many_orbits.pdf}
\caption{\Gus{update figure} We report the 95\uth minus 5\uth percentile of
the error in the measured action ($\Delta J_i$) from coordinate system errors
for three orbits with low-, medium-, and high-$J_z$ values (blue, orange, and
red, respectively). The {\em left}, {\em center}, and {\em right} panels show
the result for $J_r$, $L_z$, and $J_z$, respectively. The {\em upper} panels
consider an offset in $z$ and the {\em lower} panels consider an offset in $x$
(equivalently, an offset in the Solar radius).}
\label{fig:many_orbit_wrong_ref}
\end{figure*}

>>>>

For the offset in the Solar radius {\em bottom panels}, the error is largest
for $J_r$, with some deviations resulting in $L_z$ and relatively small
deviations in $J_z$. In the {\em bottom middle} and {\em bottom right} panels
all three lines overlap.

\begin{figure*}
\plotone{fig/schmactions_many_orbits.pdf}
\caption{We report the 95\uth minus 5\uth percentile of the error in the
measured action ($\Delta J_i$) from coordinate system errors for the thin,
thick, and halo orbits (Table~\ref{tab:orbits}). The {\em left}, {\em center},
and {\em right} panels show the result for $J_r$, $L_z$, and $J_z$,
respectively. The {\em upper} panels consider an offset in $z$ and the {\em
lower} panels consider an offset in $x$ (equivalently, an offset in the Solar
radius).}
\label{fig:many_orbit_wrong_ref}
\end{figure*}
